### 2014-10-24 PrivacyProtection-2014-09-09.tex
refactored figure threat example

\subsubsection{Threats}
This section outlines the potential threats (Figure \ref{figure:Live+Gov Threats}) for Citizen privacy in the proposed monitoring and mining System.

@@

\input{./figures/LG-Threats}
\input{./figures/Threat-Example-1}
\input{./figures/Threat-Example-2}
\input{./figures/ThreatTable}

>>>>

This section outlines the potential threats (Figure \ref{figure:Live+Gov Threats}) for Citizen privacy in the proposed monitoring and mining System.

@@

\input{./figures/LG-Threats}
\input{./figures/Threat-Example}
\input{./figures/ThreatTable}
